% SPDX-License-Identifier: GPL-3.0-or-later OR CC-BY-SA-4.0
\section{App Details Page}\label{sec:app-details-page} %%##$section-title>>
%%!!intro<<
\textbf{App Details} page consists of 11 (eleven) tabs. It describes almost every bit of information
an application usually has, including all attributes from its manifest,
\hyperref[ch:app-ops]{application operations} (app ops), signing information, libraries, and so on.
%%!!>>

\subsection{Colour Codes}\label{subsec:app-details-colour-codes} %%##$colour-codes-title>>
%%!!colour-codes<<
List of colours used in this page, and their meaning:
\begin{itemize}
    \item \colorbox{uninstalled-day}{\textcolor{black}{Red (day)}} / \colorbox{uninstalled-night}{\textcolor{white}{dark red (night)}}
    -- Denotes any app ops or permissions having the dangerous flag, or any components blocked
    within App Manager, or any unsupported but required features.

    \item \colorbox{disabled-day}{\textcolor{black}{Light red (day)}} / \colorbox{disabled-night}{\textcolor{white}{very
    dark red (night)}} -- Denotes the components disabled outside of App Manager, or any unsupported
    but optional features.

    \begin{tip}{Note}
        A component marked as disabled does not always mean that it is disabled by the user: It could also be disabled
        by the system or marked as disabled in its manifest. The components of a disabled application are also
        considered disabled by the system (and App Manager).
    \end{tip}

    \item \colorbox{tracker-day}{\textcolor{black}{Vivid orange (day)}} / \colorbox{tracker-night}{
        \textcolor{white}{very dark orange (night)}} -- Denotes the tracker components

    \item \colorbox{AMSoftMagenta}{\textcolor{black}{Soft magenta (day)}} / \colorbox{AMVeryDarkViolet}{
        \textcolor{white}{very dark violet (night)}} -- Denotes the running services.

    \item \colorbox{AMDarkCyan}{\textcolor{black}{Dark cyan}}  -- Used in the tracker-indicator tag
    to denote that all the trackers in the application are blocked.
\end{itemize}
%%!!>>

\subsection{App Info Tab}\label{subsec:app-info-tab} %%##$app-info-tab-title>>
%%!!app-info-tab<<
\textbf{App Info} tab contains general information about an application. It also lists many actions that can be
performed within this tab.
%%!!>>

\subsubsection{General Information}\label{subsubsec:app-info-general-information} %%##$app-info-general-information-title>>
%%!!app-info-general-information<<
The list below is in the same order as listed in the App Info tab.
\begin{itemize}
    \item \textbf{Application Icon.} The application icon. If the application does not have an icon, the system default
    icon will be displayed. It is also possible to verify the APK signature via SHA or MD5 sums stored in the clipboard
    by simply clicking on it.

    \item \textbf{Application Label.} The application label or the name of the application.

    \item \textbf{Package Name.} The name of the application package. Clicking on the name stores it in the clipboard.

    \item \textbf{Version.} The application version is divided into two parts. The first part is called \textit{version
    name}. The format of this part varies but often consists of multiple integers separated by dots. The second part
    is called \textit{version code}. It is enclosed by the first brackets. The version code is an integer used to
    differentiate between application versions (since a version name can be unreadable to a machine). In general,
    a new version of an application has higher version code than the old ones. For example, if \texttt{123} and
    \texttt{125} are two version codes of an application, we can say that the latter is more updated than the former
    because the version code of the latter is higher. An application that serves different APK files for the same version
    on different platforms (mobile, tabs, desktops, etc.) or architectures (32/64 bit, ARM or Intel), the version
    numbers can be misleading as they often add prefixes for each platform.

    \item \textbf{Tags.} (Also known as tag clouds) Tags include the most basic, concise and useful information of an
    application. See \Sref{subsubsec:tags} for a complete list of tags shown here.

    \item \textbf{Horizontal Action Panel.} An action panel consisting of various actions that can be carried out for
    the application. See \Sref{subsubsec:horizontal-action-panel} for a complete list of actions available here.
    Additional actions are available in the \hyperref[subsubsec:app-info-options-menu]{options menu}.

    \item \textbf{Paths \& Directories.} Contains various information regarding application paths
    including \textit{app directory} (where the APK files reside), \textit{data directories}
    (internal, device protected and externals), and \textit{JNI library directory} (if present).
    JNI libraries are used to invoke native codes usually written in C/C++. Use of native library
    can make the application run faster or help an application use third-party libraries written
    using languages other than Java like in most games. The directories can be opened via file
    managers provided they support it and have the necessary permissions, by clicking on the launch
    button on the right-hand side of a directory item.

    \item \textbf{Data Usage.} Amount of data used by the application as reported by the operating system. Depending on
    Android version, this may require a wide range of permissions including \textit{Usage Access} and \textit{Telephony}
    permissions.

    \item \textbf{Storage \& Cache.} Displays information regarding the size of the application (APK files, optimised
    files), data and cache. In older devices, size of external data, cache, media and OBB folders are also displayed.
    This part remains hidden if \textit{Usage Access} permission is not granted in the newer devices.

    \item \textbf{More Info.} Displays other information such as--
    \begin{itemize}
        \item \textbf{SDK.} Displays information related to the Android SDK: \textit{Max} denotes
        the target SDK and \textit{Min} denotes the minimum SDK (the latter is not available in
        Android Lollipop). If the target SDK value is less than the platform SDK (i.e., the highest
        SDK the current operating system supports), the application will run in the compatibility
        mode. This means the application may have access to certain features that are unavailable or
        restricted in a newer version of Android, which can be a security and/or privacy issue. SDK
        is also known as \textbf{API Level}.\\
        \seealsoinline{\href{https://en.wikipedia.org/wiki/Android_version_history\#Overview}{Android Version History}}

        \item \textbf{Flags.} The application flags used at the time of building the application. For a complete list of
        flags and what they do, read the
        \href{https://developer.android.com/reference/android/content/pm/ApplicationInfo\#flags}{official documentation}.

        \item \textbf{Date Installed.} The date when the application was first installed.

        \item \textbf{Date Updated.} The date when the application was last updated. This is the same as \textit{Date Installed}
        if the application hasn't been updated.

        \item \textbf{Process Name.} The name of the process if it is different from the package
        name. Process name is set when an application is being started by the system, and is usually
        the same as the package name.

        \item \textbf{Installer App.} The application that installed this application. The installer
        application may not always be the same as the application that installed this application,
        because Android allows setting an arbitrary value for this field. In Android 11 onwards, the
        actual installer application is also stored by the system which can be accessed by clicking
        the ``Info'' button on the right-hand side of the item. The field will not be visible if the
        installer application is not reported by the system (e.g., due to the installer application
        being uninstalled or hidden). Installer application may be granted additional privileges by
        the system so that it can control certain behaviour of the application it installs.

        \item \textbf{User ID.} The unique user ID set by the system to the application. For shared
        applications, the same user ID is assigned to multiple applications having the same
        \textit{Shared User ID}.

        \item \textbf{Shared User ID.} Applicable for applications that are shared together. The shared application must
        have the same \hyperref[subsec:signatures-tab]{signatures}.

        \item \textbf{Primary ABI.} Architecture supported by this platform for this application.

        \item \textbf{Zygote preload name.} Responsible for preloading application code and data shared across all the
        isolated services that uses app zygote.

        \item \textbf{Hidden API enforcement policy.} Since Android 9, many methods and classes in Android framework
        have been made inaccessible to the third-party applications through hidden API enforcement policy. It has the
        following options:
        \begin{itemize}
            \item \textit{Default.} Based on the type of application. For system applications, it should be disabled,
            and for others, it should be enforced.
            \item \textit{None/disabled.} The application has full access to the hidden API as it used to be before
            Android 9.
            \item \textit{Warn.} Same as above, except that warnings will be logged each time the application accesses
            the hidden API. This is mostly unused.
            \item \textit{Enforce.} The application cannot access hidden API, either dark-grey list or blacklist, or
            both of them. This is the default option for the third-party applications in Android 9 onwards unless the
            application is whitelisted by the OEM or the vendor.
            \begin{warning}{Warning}
                Hidden API enforcement policy is not properly implemented in Android and can be bypassed by the
                application. As a result, this value should not be trusted.
            \end{warning}
        \end{itemize}

        \item \textbf{SELinux.} Mandatory access control (MAC) policy set by the operating system via SELinux.

        \item \textbf{Main Activity.} The main entry point to the application. This is only visible if the application has
        \hyperref[subsubsec:activities]{activities} and any of those are openable from the Launcher. There's also a
        launch button on the right-hand side which can be used to launch this activity.
    \end{itemize}
\end{itemize}
%%!!>>

\subsubsection{Tags}\label{subsubsec:tags} %%##$tags-title>>
%%!!tags-list<<
\begin{itemize}
    \item \textbf{Tracker info.} Number of tracker components in the application (e.g., \textit{5 trackers}) The colour
    of the tag appears orange if the trackers are unblocked and dark cyan if they are blocked in App Manager.
    Clicking on the tag opens a dialog containing the list of tracker components which can also be blocked or unblocked
    provided App Manager has sufficient privileges.

    \item \textbf{Application type.} User application or system application. For a system
    application, it displays whether the application is an updated version of the system application
    or the application is installed systemless-ly via Magisk.

    \item \textbf{Split APK info.} Number of splits in the APK excluding the base APK (e.g., \textit{5 splits}).
    Clicking on the tag opens a dialog containing a few additional information, such as name, type, and size.

    \item \textbf{Debuggable.} The application can be debugged over ADB\@. Debuggable applications can enjoy certain
    functions unavailable to a regular application. The data of the application might be accessible via ADB (e.g.\ using
    \texttt{run-as} command) without any additional permissions.

    \item \textbf{Test only.} The application is a test-only application. Test-only applications can enjoy certain
    functions unavailable to a regular application. The data of the application might be accessible via ADB (e.g.\ using
    \texttt{run-as} command) without any additional permissions.

    \item \textbf{No code.} The application does not have any code associated with it i.e., DEX files aren't present.
    In some system applications, the actual code might be located in another place.

    \item \textbf{Large heap.} The application has requested large heap size i.e., more space in memory (RAM) is
    requested for dynamic allocation. It is still up to the operating system to decide whether to allocate large space
    for the application. App Manager, for example, requests large heap size because it needs to load an entire APK
    into memory while scanning an APK\@.

    \item \textbf{Open links.} The application may open certain links from any applications. If the
    application can open any links by default, the color of the tag would be red, dark cyan if
    otherwise. Clicking on the tag opens a dialog with the supported hosts or domains listed. In
    Android 12 onwards, it displays an option to enable or disable opening links by default provided
    App Manager has sufficient permissions. Otherwise, it displays an option to open the system
    settings page for the application.

    \item \textbf{Running.} One or more services of the application is currently running in the
    background. Clicking on the tag opens a dialog containing the list of running services. Clicking
    on any services opens the log viewer with default filter set to the UID associated with the
    service (which can be different from the UID of the application if it is running in a separate
    or isolated process) provided the log viewer feature is enabled. There's also an option to
    force-stop the application.

    \item \textbf{Stopped.} The application is force stopped. This may not prevent it from running automatically later.

    \item \textbf{Disabled.} Denotes that the application is disabled (hidden from the launcher).

    \item \textbf{Suspended.} Denotes that the application is suspended (grayed out in the launcher).

    \item \textbf{Hidden.} Denotes that the application is hidden (hidden from the launcher).

    \item \textbf{MagiskHide.} MagiskHide is enabled for the application. Clicking on the tag opens
    a dialog containing the list of process names within the application that can be added to or
    removed from the MagiskHide list.

    \item \textbf{MagiskDenyList.} The application is present in Magisk DenyList. Clicking on the
    tag opens a dialog containing the list of process names within the application that can be added
    to or removed from Magisk DenyList.

    \item \textbf{WX.} The application violates the ``W\textasciicircum{}X policy'' and is capable
    of writing and executing in the same directory or in the same portion of memory. This allows the
    execution of arbitrary executables either by the modification of executables embedded within the
    application or by downloading them from the Internet.\\
    \seealsoinline{\href{https://en.wikipedia.org/wiki/W\%5EX}{W\textasciicircum{}X in Wikipedia}}

    \item \textbf{Bloatware.} The application may be a known bloatware. Clicking on the tag opens a
    dialog containing detailed information in addition to suggestions (if available).

    \item \textbf{KeyStore.} The application has items in the Android KeyStore. Clicking on the tag opens a dialog
    containing all the KeyStore files that belong to the application.

    \item \textbf{Backup.} The application was backed up using App Manager at least once. Clicking on the tag
    opens a dialog containing all the available backups along with metadata.

    \item \textbf{No battery optimisation.} Battery optimisation is disabled for the application. It is possible to
    re-enable battery optimisation by clicking on the tag.

    \item \textbf{Sensors disabled.} Sensors are disabled for the application. Sensors are disabled
    for most applications by default.

    \item \hyperref[sec:net-policy]{\textbf{Net policy.}} Network policy (e.g., background data usage) is configured
    for the application. Clicking on the tag displays a dialog containing the supported policies for the platform
    along with the options to configure them.

    \item \hyperref[sec:terminologies]{\textbf{SSAID.}} Clicking on the tag opens a dialog containing the current
    SSAID assigned to the application. It is also possible to reset/regenerate the SSAID if needed.

    \item \textbf{SAF.} Denotes that the application has been granted to access one or more storage locations or
    files i.e.\ URIs via Storage Access Framework (SAF). Clicking on the tag opens a dialog containing the list of
    granted URIs.

    \item \textbf{Play App Signing.} Indicates that the application might be signed by Google.

    \item \textbf{Xposed.} Indicates that the application may be an Xposed module. Clicking on the
    tag displays a dialog with additional information.

    \item \textbf{Static Shared Library.} Denotes that the application serves as a static shared
    library for one or more applications. Clicking on the tag opens a dialog containing a list of
    installed versions of the library along with an option to uninstall them.
    \begin{tip}{Notice}
        The trichrome library (supplied by Google Chrome, Vanadium or similar projects) is currently
        the only known static shared library on Android.
    \end{tip}
\end{itemize}
%%!!>>

\subsubsection{Horizontal Action Panel}\label{subsubsec:horizontal-action-panel} %%##$horizontal-action-panel-title>>
%%!!horizontal-action-panel<<
Horizontal Action Panel, as described in the previous section, consists of various application-related actions, such as--
\begin{itemize}
    \item \textbf{Launch.} Launch the application provided it has a launcher \hyperref[subsubsec:activities]{activity}.

    \item \textbf{Freeze.} Freeze the application. This button is not displayed if it is already frozen or the user
    does not have enough privileges. After the application is frozen, it may be hidden from the app drawer depending on
    how it was configured. Shortcuts configured by the application may also be removed. The application may only be
    unfrozen via App Manager, \texttt{pm} command or any other tools that offer such a feature. Long clicking on the
    button opens a dialog where a shortcut can be configured to quickly freeze or unfreeze the application.

    \item \textbf{Uninstall.} Uninstall the application with a prompt. In the dialog prompt, it is possible to uninstall
    updates of a system application, or if App Manager has enough privileges or the operating system supports it, it is
    possible to uninstall the application without clearing its data and signature. For the latter case, the installed
    application must match the signature with the previously installed application if it is installed again.
    \begin{tip}{Tips}
        A better way to reinstall an application with a different signature would be to back up its data using App
        Manager and restore it again after installing the application instead of opting to preserving data and signature
        of the application during uninstallation as this option may cause undefined behaviour in the future.
    \end{tip}

    \item \textbf{Unfreeze.} Unfreeze the application. This button is not displayed if it is already enabled or the user
    does not have enough privileges. Similar to the \textit{Freeze} button, long clicking on the button opens a dialog
    where a shortcut can be configured to quickly freeze or unfreeze the application.

    \item \textbf{Force Stop.} Force-stop the application.

    \item \textbf{Clear Data.} Clear data from the application. This includes any information stored in the internal
    and, recently, the external directories, including accounts (if set by the application), cache, etc. Clearing data
    from App Manager, for example, removes all the rules (the blocking is not removed though) saved within the
    application (Which is why you should always take backups of your rules). This button is not displayed if the user
    does not have enough privileges.

    \item \textbf{Clear Cache.} Clear the application cache. If the application is running during the operation, the
    cache may not be cleared as expected.

    \item \textbf{Install.} Install the application, only displayed if the application hasn't
    already been installed.

    \item \textbf{What's New.} Displayed for an external application if an older version of it is
    already installed. Clicking on this button opens a dialog containing the differences between
    this and the installed version in a version control manner. Changes include \textit{version},
    \textit{trackers}, \textit{permissions}, \textit{components}, \textit{signatures} (only checksum
    changes), \textit{features}, \textit{shared libraries} and \textit{SDK}.

    \item \textbf{Update.} Displayed if the application has a higher version code than the installed application.

    \item \textbf{Reinstall.} Displayed if the application has the same version code as the installed application.

    \item \textbf{Downgrade.} Displayed if the application has a lower version code than the installed application.

    \item \textbf{Manifest.} Opens the application's manifest file in a separate page. If the
    application has more than one split, it will display the list of split APK files, and clicking
    on an item will open the corresponding manifest file instead.

    \item \textbf{Scanner.} Scan the application in order to list potential trackers and libraries.
    It also scans the file using VirusTotal and fetch results from Pithus if configured.\\
    \seealsoinline{\hyperref[sec:scanner-page]{Scanner page}}

    \item \textbf{Shared Prefs.} Displays a list of shared preferences used by the application.
    Clicking on a preference item in the list opens the \hyperref[sec:shared-preferences-editor-page]{Shared Preferences
    Editor page}. This option is only visible if the user has the required privileges.

    \item \textbf{Databases.} Displays a list of databases used by the application. Clicking on an
    item opens a list of activities that can open the database. This option is only visible if the
    user has the required privileges.

    \item \textbf{F-Droid.} Open the application in the selected \textit{F-Droid} client.

    \item \textbf{Store.} Open the application in \textit{Aurora Store}. The option is only visible if \textit{Aurora
    Store} is installed.
\end{itemize}
%%!!>>

\subsubsection{Options Menu}\label{subsubsec:app-info-options-menu} %%##$app-info-options-menu-title>>
%%!!app-info-options-menu<<
Options-menu is located in the top-right corner of the page. A complete description of the options present there are
given below:
\begin{itemize}
    \item \textbf{Share.} Share button can be used to share the APK or (if the application is has multiple splits, OBB
    files or any dependencies) \textit{APKS} file extracted from the application.

    \item \textbf{Refresh.} Refresh the App Info tab.

    \item \textbf{View in Settings.} Open the application in Android Settings.

    \item \textbf{Backup/restore.} Open the backup/restore dialog.

    \item \textbf{Export blocking rules.} Export rules configured for the application within App Manager.

    \item \textbf{Open in Termux.} Open the application in Termux. This actually runs \texttt{su - user\_id} where
    \texttt{user\_id} denotes the application's kernel user ID (described in \Sref{subsubsec:app-info-general-information}).
    This option is only visible to the root users. See \Sref{subsubsec:config-termux} to learn how to configure Termux
    to run commands from third-party applications.

    \item \textbf{Run in Termux.} Open the application via \texttt{run-as package\_name} in Termux. This is only
    applicable to the debuggable applications and works for both root and ADB users. See \Sref{subsubsec:config-termux}
    to learn how to configure Termux to run commands from third-party applications.

    \item \textbf{MagiskHide.} Open a dialog containing the list of process names within the application that can be added
    or removed from the MagiskHide list.

    \item \textbf{Magisk DenyList.} Open a dialog containing the list of process namees within the application that can be
    added or removed from Magisk DenyList.

    \item \textbf{Battery optimisation.} Enable/disable battery optimisation for this application.

    \item \textbf{Sensors.} Enable/disable sensors for this application.

    \item \hyperref[sec:net-policy]{\textbf{Net policy.}} Configure network policy (e.g., background data usage) for the
    application.

    \item \textbf{Extract Icon.} Extract and save the application's icon in the shared storage.

    \item \textbf{Optimize.} Perform optimisation for this application. This option is for advanced
    users only.

    \item \textbf{Add to profile.} Add the application to one of the configured \hyperref[sec:profile-page]{profiles}.

    \item \textbf{Install for….} Install the application for another user and/or in the work profile if configured.
\end{itemize}
%%!!>>

\subsubsection{Configuring Termux}\label{subsubsec:config-termux} %%##$config-termux-title>>
%%!!config-termux<<
By default, Termux does not allow running commands from a third-party application. To use this option, Termux v0.96 or
later is required and \texttt{allow-external-apps=true} must be added in \texttt{\textasciitilde/.termux/termux.properties}.

\begin{tip}{Info}
    Enabling this option does not weaken Termux' security. The third-party applications still need to ask the user to
    allow running arbitrary commands in Termux.
\end{tip}
%%!!>>

\subsection{Component Tabs}\label{subsec:component-tabs} %%##$component-tabs-title>>
%%!!component-tabs<<
\textbf{Activities}, \textbf{Services}, \textbf{Receivers} (i.e., broadcast receivers) and
\textbf{Providers} (e.g., content providers) are collectively known as the application components,
because they offer similar features and share similar properties. For example, they all have a
\textit{name}, a \textit{label}, an \textit{icon}, can be enabled or disabled, and can be executed
via \textit{Intent}. Application components are the building blocks of an application and must be
declared in the application manifest (with a few exceptions). Application manifest is a file where
application specific metadata are stored. The Android operating system learns what to do with the
application by reading the metadata.

Colours used in these tabs are explained in \Sref{subsec:app-details-colour-codes}. It is also
possible to sort the list of components to display blocked or tracker components on top of the list
via the \textbf{Sort} option located in the three-dots menu.
%%!!>>

\subsubsection{Activities}\label{subsubsec:activities} %%##$activities-title>>
%%!!activities<<
\textbf{Activities} are the windows or pages that can be uniquely identified by the Android operating system (e.g.,
\textit{Main page} and \textit{App Details page} are two activities). Each activity can have multiple UI components
known as \textit{widgets} or \textit{fragments}, and each component can be nested or placed on top of each other. The
developer can also choose to open external files, links, etc. within an activity using a method called
\textit{intent filters}. For example, when you open a file in your file manager, either your file manager or the
operating system scans the intent filters via PackageManager, find the activities capable of opening the file, and
list those activities so that you can choose your preferred activity.

Activities that are \textit{exportable} can be opened by any third-party applications. However, Some
activities may require permissions, and only an application having those permissions can open them.
In the \textit{Activities} tab, certain activities can be launched via the \textbf{Launch} button.
If it is necessary to supply additional information, such as Intent extras, data or action, long
clicking on the \textbf{Launch} button opens the \hyperref[sec:interceptor-page]{Activity Interceptor}
page which provides such features.

\begin{tip}{Tip}
    No-root users can grant \texttt{android.permission.WRITE\_SECURE\_SETTINGS} via ADB to launch
    \textit{non-exportable} activities.
\end{tip}

\begin{tip}{Notice}
    If launching an activity throws an error, it may have certain dependencies which are not met
    (e.g., \textit{App Details} page in App Manager cannot be launched using the launch button,
    because it requires a package name). Since the dependencies cannot be inferred programmatically,
    the activity may not be opened from App Manager by default.
\end{tip}

It is also possible to create shortcuts of an activity-launch using the \textbf{Create shortcut}
button. If you need to supply additional information, you can create a shortcut from the Activity
Interceptor page instead.

\begin{danger}{Caution}
    If you uninstall App Manager, all shortcuts created by App Manager will be lost.
\end{danger}
%%!!>>

\subsubsection{Services}\label{subsubsec:details:servcies} %%##$servcies-title>>
%%!!servcies<<
Unlike \hyperref[subsubsec:activities]{activities} that users can see, \textbf{Services} handle background tasks. For example,
if you're downloading a video from the internet using your phone's Internet browser, the Internet browser is using a
\textit{foreground service} to download the content.

When an activity is closed or removed from the \textit{Recents} page, it may be destroyed
immediately depending on the amount free memory the phone has, battery statistics, or how the
activity is configured. But services can be run indefinitely if desired. If more services run in the
background, the phone may become slower due to the shortage of memory and/or processing power, and
the phone's battery will be drained more quickly. Newer versions of Android come with a battery
optimisation feature enabled by default for all applications. With this feature enabled, the system
can randomly terminate any service depending on the amount of resources the system has or the
service requires. However, foreground services (i.e., services that run with a fixed notification,
such as music player or downloader) are not typically terminated unless the system is very low on
resources (memory, battery, etc.). Certain stock ROMs can offer more aggressive optimisation. MIUI,
for example, has a very aggressive optimisation feature known as the \textit{MIUI optimisation}.

Both activities and services are run in the same \href{https://stackoverflow.com/questions/7597742}{looper} called
the main looper, which means the services do not really run in the background. It is the task of the developer to
ensure this. How do the application communicate with the services? It uses
\hyperref[subsubsec:app-details-receivers]{broadcast receiver} or Binder.
%%!!>>

\subsubsection{Receivers}\label{subsubsec:app-details-receivers} %%##$receivers-title>>
%%!!receivers<<
\textbf{Receivers} (also called \textit{broadcast receivers}) can be used to trigger execution of certain tasks when
certain events occur. These components are called broadcast receivers, because they are executed as soon as a broadcast
message is received. These broadcast messages are sent using a method called \textit{Intent}. Intent is a special
feature in Android that can be used to open applications (i.e., activities), run services and send broadcast messages.
Therefore, like \hyperref[subsubsec:activities]{activities}, broadcast receivers use \textit{intent filters} to receive
the desired broadcast messages. Broadcast messages can be sent by the system or the application itself. When a broadcast
message is sent, the corresponding receivers are activated by the system so that they can execute tasks. For example, if
your phone is low on resources, it may freeze or experience lags for a moment after you enable mobile data or connect it
to the Wi-Fi. This is because broadcast receivers that can receive \texttt{android.net.conn.CONNECTIVITY\_CHANGE} are
activated by the system as soon as the data connection is enabled. Since many applications typically use this intent
filter, they are all activated almost immediately by the system which causes the freezing or lags.

Receivers can also be used for inter-process communication (IPC), i.e., it can be used to communicate across multiple
applications or even different components of a single application.
%%!!>>

\subsubsection{Providers}\label{subsubsec:providers} %%##$providers-title>>
%%!!providers<<
\textbf{Providers} are primarily used for data management. For example, when you save an APK file or
export rules in App Manager, it uses a content provider called \texttt{.fm.FmProvider} to save the
APK or export the rules. There are many providers, including the ones provided by the system, that
can be used to manage various content-related tasks, such as database management, tracking,
searching, etc. Each provider has a field called \textit{Authority} which is unique to the
application in the entire Android ecosystem just as the package name.
%%!!>>

\subsubsection{Additional Features for Rooted Phones} %%##$additional-features-for-rooted-phones-title>>
%%!!additional-features-for-rooted-phones<<
Unlike the no-root users who are mostly spectators in these tabs, root users can perform various operations.
%%!!>>

\paragraph{Blocking Components.} %%##$blocking-components-title>>
%%!!blocking-components<<
On the right-most side of each component item, there is a switch which can be used to toggle the blocking status of that
particular component. If \hyperref[subsubsec:instant-component-blocking]{Instant Component Blocking} is not enabled or
blocking is never applied to the application before, it is required to apply the changes using the \textbf{Apply rules}
option in three-dots menu. It is also possible to remove the already-applied rules using the same option (which would be
read as \textbf{Remove rules} this time).

It is also possible to block the component using one of the several methods by long clicking on the button.

\seealsoinline{\hyperref[sec:faq:app-components]{FAQ: App Components}}
%%!!>>

\paragraph{Blocking Trackers.}\label{par:appdetails:blocking-trackers} %%##$blocking-trackers-title>>
\phantomsection
%%!!blocking-trackers<<
It is possible to disable tracker components using the \textbf{Block tracker} option in the three-dots menu. All tracker
components will be blocked regardless of the tab you're currently in.

\begin{tip}{Info}
    Tracker components are a subset of application components. Therefore, they are blocked using the same method used
    for blocking any other components.
\end{tip}

\begin{amseealso}
    \item \hyperref[subsec:tracker-classes-versus-tracker-components]{FAQ: Tracker classes versus tracker components}
    \item \hyperref[sec:scanner-page]{Scanner Page}
    \item \hyperref[subsec:block-unblock-trackers]{1-Click Ops Page: Block/Unblock Trackers}
\end{amseealso}
%%!!>>

\subsection{Permission Tabs}\label{subsec:permission-tabs} %%##$permission-tabs-title>>
%%!!permission-tabs<<
\textbf{App Ops}, \textbf{Uses Permissions} and \textbf{Permissions} tabs are related to permissions. In Android
communication across applications or processes not having the same identity (known as \textit{shared ID}) often
require permissions. These permissions are managed by the permission controller. Some permissions are considered
\textit{normal} permissions which are granted automatically if they appear in the application manifest, but
\textit{dangerous} and \textit{development} permissions require confirmation from the user. Colours used in these tabs
are explained in \Sref{subsec:app-details-colour-codes}.
%%!!>>

\subsubsection{App Ops}\label{subsubsec:app-ops} %%##$app-ops-title>>
%%!!app-ops<<
\textbf{App Ops} stands for \textbf{Application Operations}. Since Android 4.3, \textit{App Ops} are used by Android to
control many system permissions. Each app op has a unique number associated with it which is displayed along with the
private name of the operation in the App Ops tab. Some app ops also have a public name. A large number of app ops are
also associated with \textit{permissions}. In this tab, an app op is considered dangerous if its associated permission
is marked as dangerous. Other information such as \textit{flags}, \textit{permission name}, \textit{permission description},
\textit{package name}, \textit{group} are also taken from the associated \hyperref[subsubsec:permissions]{permission}.
Others may include the following:
\begin{itemize}
    \item \textbf{Mode.} It describes the current authorisation status which can be \textit{allow}, \textit{deny} (a
    rather misnomer, it simply means error), \textit{ignore} (it actually means deny), \textit{default} (inferred from
    a list of defaults set internally by the vendor or the AOSP), \textit{foreground} (in newer Android versions, it
    means the app op can only be used when the application is running in foreground), and some custom modes set by the
    vendors (MIUI uses \textit{ask}, for example).

    \item \textbf{Duration.} The amount of time this app op has been used (there can be negative durations whose
    use cases are currently unknown to me).

    \item \textbf{Accept Time.} Last time the app op was accepted.

    \item \textbf{Reject Time.} Last time the app op was rejected.
\end{itemize}

\begin{tip}{Info}
    Contents of this tab are visible to no-root users if \texttt{android.permission.GET\_APP\_OPS\_STATS} is granted via ADB\@.
\end{tip}

There is a toggle button next to each app op item which can be used to allow or deny (ignore) it. Other supported modes
can also be set by long clicking on the toggle button. If the desired app op is not listed in the tab,
\textit{Set custom app op} option in the menu can be used instead. It is also possible to reset the changes
using the \textit{Reset to default} option, or deny all the dangerous app ops using the corresponding option in the menu.
Due to the nature how app ops work, the system may take some time to apply them.

\begin{tip}{Tip}
    Denying certain app ops may cause the application to misbehave. If all attempts fail, \textit{reset to default}
    option can be used as the last resort.
\end{tip}

It is possible to sort the list in ascending order by app op names and the associated unique numbers (or values), or
list the denied app ops first using the corresponding sorting options.

\seealsoinline{\hyperref[ch:app-ops]{Appendix: App Ops}}
%%!!>>

\subsubsection{Uses Permissions} %%##$uses-permissions-title>>
%%!!uses-permissions<<
\textbf{Uses Permissions} are the permissions used by the application. This is named so because they are specified in
the manifest using \texttt{uses-permission} tags. Information such as \textit{flags}, \textit{permission name},
\textit{permission description}, \textit{package name}, \textit{group} are taken from the associated
\hyperref[subsubsec:permissions]{permission}.

Privileged users can grant or revoke the \textit{dangerous} and \textit{development} permissions via the toggle button
on the right side of each permission item. It is also possible revoke dangerous permissions all at once using the
corresponding option in the menu. Only these two types of permissions can be revoked because Android does not allow
the modification of \textit{normal} permissions (which most of them are). It might still be possible to revoke them
by editing \texttt{runtime-permissions.xml} itself, but whether this is a possibility is still being investigated.

\begin{tip}{Info}
    Since dangerous permissions are revoked by default by the system, revoking all dangerous permissions is the same as
    resetting all the permissions.
\end{tip}

It is possible to sort the permissions by their name (in ascending order) or choose to display denied or dangerous
permissions at first using the corresponding options in the menu.
%%!!>>

\subsubsection{Permissions}\label{subsubsec:permissions} %%##$permissions-title>>
%%!!permissions<<
\textbf{Permissions} are usually custom permissions defined by the application itself. These type of
permissions are marked as \textit{Internal} permissions. It also contains permissions declared by
other applications which are marked as \textit{External} permissions. An external permission can be
specified in an \textit{exported} application component so that another application may invoke the
component only if it holds the permission. Below is a complete description of each item displayed in
this tab:
\begin{itemize}
    \item \textbf{Name.} A permission has a unique name (e.g., \texttt{android.permission.INTERNET})
    that multiple applications can request. The application that declared the permission is
    automatically granted and cannot be revoked.

    \item \textbf{Icon.} Each permission can have a custom icon. The other permission tabs do not have any icon because
    they do not contain any icon in the application manifest.

    \item \textbf{Description.} This optional field describes the permission. If there isn't any description associated
    with the permission, the field is not displayed.

    \item \textbf{Flags.} (Uses the flag symbol or \textbf{Protection Level} name) This describes various permission
    flags such as \textit{normal}, \textit{development}, \textit{dangerous}, \textit{instant}, \textit{granted},
    \textit{revoked}, \textit{signature}, \textit{privileged}, etc.

    \item \textbf{Package Name.} Denotes the package name associated with the permission, i.e.\ the package that defined
    the permission.

    \item \textbf{Group.} The group name associated with the permission (if any). Several related permissions can often
    be grouped together.
\end{itemize}
%%!!>>

\subsection{Signatures Tab}\label{subsec:signatures-tab} %%##$signatures-tab-title>>
%%!!signatures-tab_1<<
\textbf{Signatures} are actually called signing information. An application is signed with one or
more signing keys by its developer before publishing it. The integrity of an application, i.e.,
whether the application is from the actual developer and has not been modified by another person,
can be checked using the signing certificate included in the APK files. This is because when an
application is modified by an unauthorised entity, the application can longer be signed with the
original signing keys since the signing keys are unknown to the entity. One way to verify the
integrity of an application is via the checksums generated from the certificates. If the developer
supplies the checksums for the signing certificates, they can be compared against the checksums
generated in the \textbf{Signatures} tab to verify the application. For example, if you have
downloaded App Manager from GitHub or Telegram Channel, you can verify whether the application was
actually released by me by simply matching the following \textit{SHA256} checksum with the one
displayed in this tab:
%%!!>>
\begin{Verbatim}
320c0c0fe8cef873f2b554cb88c837f1512589dcced50c5b25c43c04596760ab
\end{Verbatim}

%%!!signatures-tab_2<<
Several hashing algorithms are used to generate checksums in this tab. They include \textit{MD5}, \textit{SHA1},
\textit{SHA256} and \textit{SHA512}.

\begin{danger}{Caution}
    Signing information should be verified using a reliable hashing algorithm, such as \textit{SHA256}.
    DO NOT rely on \textit{MD5} or \textit{SHA1} checksums as they are known to generate the same
    checksums for multiple certificates.
\end{danger}
%%!!>>

\subsection{Uses Features tab}\label{subsec:uses-features-tab} %%##$uses-features-tab-title>>
%%!!uses-features-tab<<
\textbf{Uses Features} tab lists the features declared by the application, such as OpenGL ES,
telephony, and leanback. Some features can be required by the application, and some features can be
optional. Required features must be present in the system along with the required version.
Otherwise, any attempt to install the application will be denied by the system. Colours used in this
tab are explained in \Sref{subsec:app-details-colour-codes}.
%%!!>>

\subsection{Configurations tab}\label{subsec:configurations-tab} %%##$configurations-tab-title>>
%%!!configurations-tab<<
\textbf{Configurations} tab lists the configurations required by the application, such as input
method type (qwerty, 12 key), touch screen type (finger, stylus, etc.), and navigation type (dial
pad, trackball, wheel). This tab is going to be empty for most applications.
%%!!>>

\subsection{Shared Libraries Tab}\label{subsec:shared-libs-tab} %%##$shared-libs-tab-title>>
%%!!shared-libs-tab<<
\textbf{Shared libraries} tab lists the legacy JAR dependencies, any static shared library
dependencies (currently, the only known cases are the Chromium-based browsers and WebViews) as well
as the JNI (Java native interface) libraries. For JNI libraries, it specifies platform
(x86/x86\_64/ARM/AArch64), architecture (32/64 bit), object type (shared object or executable), etc.
%%!!>>
