\chapter{Changelogs}\label{ch:changelogs}

\section{v2.5.20 (375)}\label{sec:v2.5.20-(375)}

\subsection{Introducing Profiles}\label{subsec:introducing-profiles}
\hyperref[sec:profile-page]{Profiles} finally closes the
\href{https://github.com/MuntashirAkon/AppManager/issues/72}{related issue}. Profiles can be used to execute certain
tasks repeatedly without doing everything manually. A profile can be applied (or invoked) either from the
\hyperref[sec:profiles-page]{Profiles page} or from the home screen by creating shortcuts. There are also some presets
which consist of debloating profiles taken from
\href{https://gitlab.com/W1nst0n/universal-android-debloater}{Universal Android Debloater}.

\paragraph{Known limitations}
\begin{itemize}
    \item Exporting rules and applying permissions are not currently working.
    \item Profiles are applied for all users.
\end{itemize}

\subsection{The Interceptor}\label{subsec:the-interceptor}
\href{https://github.com/MuntashirAkon/intent-intercept}{Intent Intercept} works as a man-in-the-middle between source
and destination, that is, when you open a file or URL with another app, you can see what is being shared by opening it
with Interceptor first. You can also add or modify the intents before sending them to the destination. Additionally,
you can double-click on any exportable activities in the Activities tab in the App Details page to open them in the
Interceptor to add more configurations.

\paragraph{Known limitation} Editing extras is not currently possible.

\subsection{UnAPKM: DeDRM the APKM files}\label{subsec:unapkm:-dedrm-the-apkm-files}
When I released a small tool called \href{https://f-droid.org/en/packages/io.github.muntashirakon.unapkm}{UnAPKM},
I promised that similar feature will be available in App Manager. I am proud to announce that you can open APKM files
directly in the App Info page or convert them to APKS or install them directly.

\subsection{Multiple user}\label{subsec:multiple-user}
App manager now supports multiple users! For now, this requires root or ADB. But no-root support is also being
considered. If you have multiple users enabled and click on an app installed in multiple profiles, an alert prompt will
be displayed where you can select the user.

\subsection{Vive la France!}
Thanks to the contributors, we have one more addition to the language club: French. You can add more languages or
improve existing translations at \href{https://hosted.weblate.org/engage/app-manager}{Weblate}.

\subsection{Report crashes}
If App Manager crashes, you can now easily report the crash from the notifications which opens the share options.
Crashes are not reported by App Manager, it only redirects you to your favourite Email client.

\subsection{Android 11}
Added support for Android 11. Not everything may work as expected though.

\subsection{App Installer Improvements}

\subsubsection{Set installation locations}
In settings page, you can set install locations such as auto (default), internal only and prefer external.

\subsubsection{Set APK installer}
In settings page, you can also set default APK installer (root/ADB only) instead of App Manager.

\subsubsection{Multiple users}
In settings page, you can allow App Manager to display multiple users during APK installation.

\subsubsection{Signing APK files}
In settings page, you can choose to sign APK files before installing them. You can also select which signature scheme
to use in the \textit{APK signing} option in settings.

\paragraph{Known limitation} Currently, only a generic key is used to sign APK files

\section{v2.5.17 (368)}

\subsection{App Installer}
As promised, it is now possible to select splits. AM also provides recommendations based on device configurations.
If the app is already installed, recommendations are provided based on the installed app. It is also possible to
downgrade to a lower version without data loss if the device has root or ADB. But it should be noted that not all app
can be downgraded. Installer is also improved to speed up the installation process, especially, for root users.
If the app has already been installed and the new (x)apk(s) is newer or older or the same version with a different
signature, AM will display a list of changes similar to \textbf{What's New} before prompting the user to install
the app. This is useful if the app has introduced tracker components, new permissions, etc.

\paragraph{Known Limitations}
\begin{itemize}
    \item Large app can take a long time to fetch app info and therefore it may take a long time display the installation prompt.
    \item If the apk is not located in the internal storage, the app has to be cached first which might also take
    a long time depending on the size of the apk.
\end{itemize}

\subsection{Scanner: Replacement for Exodus Page}
Exodus page is now replaced with scanner page. \hyperref[sec:scanner-page]{Scanner page} contains not only a list of
trackers but also a list of used libraries. This is just a start. In the future, this page will contain more in depth
analysis of the app.

\subsection{Introducing System Config}
System Config lists various system configurations and whitelists/blacklists included in Android by either OEM/vendor,
AOSP or even some Magisk modules. Root users can access this option from the overflow menu in the main page.
There isn't any official documentation for these options therefore it's difficult to write a complete documentation
for this page. I will gradually add documentations using my own knowledge. However, some functions should be
understandable by their name.

\subsection{More Languages}
Thanks to the contributors, AM now has more than 12 languages. New languages include Bengali, Hindi, Norwegian, Polish,
Russian, Simplified Chinese, Turkish and Ukrainian.

\subsection{App Info Tab}
More tags are added in the \hyperref[subsec:app-info-tab]{app info tab} such as \textbf{KeyStore} (apps with KeyStore
items), \textbf{Systemless app} (apps installed via Magisk), \textbf{Running} (apps that are running). For external apk,
two more options are added namely \textbf{Reinstall} and \textbf{Downgrade}. Now it is possible to share an apk via
Bluetooth. For system apps, it is possible to uninstall updates for root/ADB users. But like the similar option in the
system settings, this operation will clear all app data. As stated above, exodus has been replaced with scanner.

\subsection{Navigation Improvements}
It's now relatively easy to navigate to various UI components using keyboard. You can use up/down button to navigate
between list items and tab button to navigate to UI components inside an item.

\subsection{Running Apps Page}
It is now possible to sort and filter processes in this tab. Also, the three big buttons are replaced with an
easy-to-use three dot menu. Previously the memory usage was wrong which is fixed in this version.

\subsection{Built-in Toybox}
Toybox (an alternative to busybox) is bundled with AM. Although Android has this utility built-in from API 23, toybox
is bundled in order to prevent buggy implementations and to support API < 23.

\subsection{Component Blocker Improvements}
Component blocker seemed to be problematic in the previous version, especially when global component blocking is enabled.
The issues are mostly fixed now.

\begin{warning}[Caution]
    The component blocking mechanism is no longer compatible with v2.5.6 due to various security issues. If you have
    this version, upgrade to v2.5.13 or earlier versions first. After that, enable
    \hyperref[subsubsec:instant-component-blocking]{global component blocking} and disable it again.
\end{warning}

\subsection{Improvements in the App Details Page}
Value of various app ops depend on their parent app ops. Therefore, when you allow/deny an app op, the parent of the app
op gets modified. This fixes the issues some users have been complaining regarding some app ops that couldn't be changed.

If an app has the target API 23 or less, its permissions cannot be modified using the \texttt{pm grant \ldots} command.
Therefore, for such apps, option to toggle permission has been disabled.

The signature tab is improved to support localization. It also displays multiple checksums for a signature.

\subsection{App Manifest}
Manifest no longer crashes if the size of the manifest is too long. Generated manifest are now more accurate than before.

\section{v2.5.13 (348)}

\subsection{Bundled App (Split APK)}
Bundled app formats such as \textbf{apks} and \textbf{xapk} are now supported. You can install these apps using
the regular installation buttons. For root and adb users, apps are installed using shell, and for non-root users,
the platform default method is used.

\paragraph{Known Limitations}
\begin{itemize}
    \item Currently \textit{all} splits apks are installed. But this behaviour is going to change in the next release.
    If you only need a few splits instead of all, extract the \textbf{APKS} or \textbf{XAPK} file, and then, create a new zip
    file with your desired split apks and replace the \textbf{ZIP} extension with \textbf{APKS}. Now, open it with AM.
    \item There is no progress dialog to display the installation progress.
\end{itemize}

\subsection{Direct Install Support}
You can now install \textbf{APK}, \textbf{APKS} or \textbf{XAPK} directly from your favourite browser or file manager.
For apps that need updates, a \textbf{What's New} dialog is displayed showing the changes in the new version.

\paragraph{Known Limitations}
\begin{itemize}
    \item Downgrade is not yet possible.
    \item There is no progress dialog to display the installation progress. If you cannot interact with the current page,
    wait until the installation is finished.
\end{itemize}

\subsection{Remove All Blocking Rules}
In the Settings page, a new option is added which can be used to remove all blocking rules configured within App Manager.

\subsection{App Ops}
\begin{itemize}
    \item App Ops are now generated using a technique similar to AppOpsX. This should decrease the loading time
    significantly in the App Ops tab.
    \item In the App Ops tab, a menu item is added which can be used to list only active app ops without including the
    default app ops. The preference is saved in the shared preferences.
\end{itemize}

\paragraph{Known Limitation} Often the App Ops tab may not be responsive. If that's the case, restart App Manager.

\subsection{Enhanced ADB Support}
ADB shell commands are now executed using a technique similar to AppOpsX (This is the \textit{free} alternative of AppOps by Rikka.).
This should dramatically increase the execution time.

\paragraph{Known Limitation} AM can often crash or become not responsive. If that's the case, restart App Manager.

\subsection{Filtering in Main Page}
Add an option to filter apps that has at least one activity.

\subsection{Apk Backup/Sharing}
Apk files are now saved as \texttt{app name\_version.extension} instead of \texttt{package.name.extension}.

\subsection{Batch Ops}
\begin{itemize}
    \item Added a foreground service to run batch operations. The result of the operation is displayed in a notification.
    If an operation has failed for some packages, clicking on the notification will open a dialog box listing the failed
    packages. There is also a \textbf{Try Again} button on the bottom which can be used to perform the operation again for the failed packages.
    \item Replaced Linux \textit{kill} with \textbf{force-stop}.
\end{itemize}

\subsection{Translations}
Added German and Portuguese (Brazilian) translations.

\paragraph{Known Limitation} Not all translations are verified yet.

\subsection{App Data Backup}
Install app only for the current user at the time of restoring backups. Support for split apks is also added.

\textit{Data backup feature is now considered unstable. If you encounter any problem, please report to me without hesitation.}
