\section{Backup/Restore}\label{sec:backup-restore}
App Manager has a modern, advanced and easy-to-use backup/restore system implemented from the scratch. This is probably
the only app that has the ability to restore not only the app or its data but also permissions and rules that you've
configured within App Manager. You can also choose to back up an app multiple times (with custom names) or for all users.

\begin{tip}{Notice}
    Backup/Restore is completely different from \textbf{Backup APK} which is also a part of the batch operations.
\end{tip}

\begin{warning}{Warning}
    As of v2.5.22, backup/restore is a beta feature (previously, it was an alpha feature). Support for old backups are
    removed as a result. From now on, backward compatibility will be provided.
\end{warning}

\subsection{Location}\label{subsec:backup-location}
Backup/restore is a part of \hyperref[subsec:batch-operations]{batch operations}. It is also located inside the
\hyperref[subsubsec:app-info-options-menu]{options menu} in the \hyperref[subsec:app-info-tab]{App Info tab}. Clicking
on \textbf{Backup/Restore} opens the \textbf{Backup Options}. The backups are currently located at
\texttt{/sdcard/AppManager}.

\begin{tip}{Note}
    If one or more selected apps don't have any backup, the \textbf{Restore} and \textbf{Delete Backup} options will not
    be displayed.
\end{tip}

\subsection{Backup Options}\label{subsec:backup-restore-backup-options}
Backup options (internally known as backup flags) let you customise the backups on the fly. However, the customisations
will not be remembered for the future backups. If you want to customise this dialog, use
\hyperref[subsubsec:settings-backup-options]{Backup Options} in the \hyperref[sec:settings-page]{Settings page}.

A complete description of backup options is given below:
\begin{itemize}
    \item \textbf{Source.} Whether to back up or restore the entire source directory. When you install an app, the APK
    files are stored inside the \texttt{/data/app/} along with any native libraries as well as some other files such as
    the ODEX and VDEX files. This directory is called \textbf{source directory} or \textbf{code path}. You can further
    customise this using the \textbf{APK only} option.

    \item \textbf{APK only.} When you enable \textbf{Source} option, the whole source directory is backed up or
    restored. Enabling this along with \textbf{Source} will only backup or restore the APK files and skip backing up the
    native libraries or ODEX and VDEX files.

    \item \textbf{Internal Data.} Whether to back up the internal data directories. These directories are located at
    \texttt{/data/user/<user\_id>} and (for Android N or later) \texttt{/data/user\_de/<user\_id>}.

    \item \textbf{External data.} Whether to back up data directories located in the internal memory as well as SD Card
    (if exists). External data directories often contain non-essential app data or media files (instead of using the
    dedicated media folder) and may increase the backup size. However, it might be essential for some apps. Although
    it isn't checked by default (as it might dramatically increase the size of the backups), you will need to check it
    in order to ensure a smooth restore of your backups.
    \begin{warning}{Caution}
        Internal data folders should always be backed up if you are going to back up the external data folders. However,
        it could be useful to back up only the external folders if the app in questions downloads a lot of assets from
        the Internet.
    \end{warning}

    \item \textbf{OBB and media.} Whether to back up or restore the OBB and the media directories located in the
    external storage or the SD Card. This is useful for games and the graphical software which actually use these
    folders.

    \item \textbf{Exclude cache.} Android apps have multiple cache directories located at every data directories (both
    internal and external). There are two types of cache: \textbf{cache} and \textbf{code cache}. Enabling this option
    excludes both cache directories from all the data directories. It is generally advised to exclude cache directories
    since most apps don't clear the cache (for some reason, the only way an app can clear its cache is by deleting the
    entire cache directory) and usually handled by the OS itself. Apps such as Telegram may use a very large cache
    (depending on the storage space) which may dramatically increase your backup size. When it is enabled, AM also
    ignores backup from the \textbf{no\_backup} directories.

    \item \textbf{Extras.} Backup/restore app permissions, net policy, battery optimization, SSAID, etc. It's enabled
    by default. Note that, blocking rules are applied \textit{after} applying the extras. So, if an item is present in
    both places, it will be overwritten (i.e., the one from the blocking rules will be used).

    \item \textbf{Rules.} This option lets you back up blocking rules configured within App Manager. This might come in
    handy if you have customised permissions or block some components using App Manager as they will also be backed up
    or restored when you enable this option.

    \item \textbf{Backup Multiple.} Whether this is a multiple backup. By default, backups are saved using their user
    ID. Enabling this option allows you to create additional backups. These backups use the current date-time as the
    default backup name, but you can also specify custom backup name using the input field displayed when you click on
    the \textbf{Backup} button.

    \item \textbf{Custom users.} Backup or restore for the selected users instead of only the current user. This option
    is only displayed if the system has more than one user.

    \item \textbf{Skip signature checks.} When taking a backup, checksum of every file (as well as the signing
    certificate(s) of the base APK file) is generated and stored in the \texttt{checksums.txt} file. When you restore
    the backup, the checksums are generated again and are matched with the checksums stored in the said file. Enabling
    this option will disable the signature checks. This option is applied only when you restore a backup. During backup,
    the checksums are generated regardless of this option.
    \begin{warning}{Caution}
        You should always disable this option to ensure that your backups are not modified by any third-party
        applications. However, this would only work if you enabled encryption.
    \end{warning}
\end{itemize}

\subsection{Backup}\label{subsec:backup-restore-backup}
Backup respects all the backup options except \textbf{Skip signature checks}. If base backups (i.e., backups that don't
have the \textbf{Backup Multiple} option) already exist, you will get a warning as the backups will be overwritten. If
\textbf{Backup Multiple} is set, you have an option to input the backup name, or you can leave it blank to use the
current date-time.

\subsection{Restore}\label{subsec:backup-restore-restore}
Restore respects all the backup options and will fail if \textbf{Source} option is set, but the backup doesn't contain
any source backups or in other cases, if the app isn't installed. When restoring backups for multiple packages, you can
only restore the base backups (see \hyperref[subsec:backup-restore-backup]{backup} section for an explanation). However,
when restoring backups for a single package, you have the option to select which backup to restore. If
\textbf{All users} option is set, AM will restore the selected backup for all users in the latter case but in the former
case, it will restore base backups for the respective users.

\begin{tip}{Notice}
    Apps that use storage access framework (SAF), SSAID or Android KeyStore works properly only after an immediate restart.
\end{tip}

\subsection{Delete Backup}\label{subsec:backup-restore-delete-backup}
Delete backup only respects \textbf{All users} option and when it is selected, only the base backups for all users will
be deleted with a prompt. When deleting backups for a single package, another dialog will be displayed where you can
select the backups to delete.

\subsection{Encryption}\label{subsec:backup-restore-encryption}
App Manager currently supports OpenPGP encryption. To enable it, you need to install an OpenPGP provider such as
\href{https://openkeychain.org}{OpenKeychain}. To configure OpenPGP provider, go to the
\hyperref[subsubsec:settings-encryption]{Settings page}.
